Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-09 analysis/paper/paper.Rmd
Edits to results section

Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019] and the Region of Practical Equivalence (ROPE) was set to -0.1 to 0.1.

@@

@@

## Effect of Journal Title

The analysis found that publications in Phytopathology were more likely to share their code but was unable to detect differences in any other journal titles.
Publications in Crop Protection and Plant Disease were less likely to share their data but no effects were detectable in any other journal title.

## Effect of Year

@@

## Effect of Impact Factor

@@

## Effect of Access Policy

>>>>

A test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019] with the Region of Practical Equivalence (ROPE) set to -0.1 to 0.1.

@@

## Code and Data Sharing Classification Scores

@@

## Analysis of Effects

The analysis found that publications in Phytopathology were more likely to share their code but undecided on any effects of any other journal titles (Median = `summarise_draws(m_f1) %>% filter(variable == "b_abbreviationPhytopathology") %>% select(median)`, 95% CI [0.78, 4.21] and can be considered as significant (0% in ROPE).
Publications in Crop Protection and Plant Disease were less likely to share their data but no effects were detectable in any other journal title.

@@

@@
